A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-02-12 manuscript.Rmd
adept readme screenshot

```{r readme-screenshot, include=FALSE}
# unfortunately css selectors won't work for pdf so we'll use png instead
readme <- here::here("images", "readme.png")
webshot2::webshot("https://github.com/aaronpeikert/repro-tutorial/",
                  file = readme,
                  selector = "div#readme",
                  zoom = 1)# higher resolution
```

>>>>

```{r readme-screenshot, include=FALSE}
# unfortunately css selectors won't work for pdf so we'll use png instead
readme <- here::here("images", "readme.png")
webshot2::webshot("https://github.com/aaronpeikert/repro-tutorial/",
                  file = readme,
                  vwidth = 1920, # height & width are not resolution
                  vheight = 1080, # but what website thinks the browser size is
                  selector = "div#readme",
                  zoom = 2) # higher resolution
```
